---
csl: british-ecological-society.csl
bibliography: landUseChangePaper.bib
citation_package: natbib
geometry: a4paper, margin=25mm, portrait
spacing: double
output:
  pdf_document:
    latex_engine: pdflatex
    keep_tex: true
    fig_caption: true
header-includes:
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage[utf8]{inputenc}
- \renewcommand{\familydefault}{phv}
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \onehalfspacing
- \raggedright


--- 


# Building future landscapes to assess impact of land use land cover change on provisioning of ecosystem services  
  
\today  
  
Reto Schmucki^1^  

^1^ CEH, Benson Lane, MacLean Building, Wallingford, OX10 8BB, UK


### Abstract 

LULC change models [@schmucki_regionally_2016] may become fundamental [@aquilue_spatial_2017] tools to accurately inform policy makers and land managers committed to sustainable development, biodiversity  conservation $\sqrt{27}$ and regional assessments of ecosystem services provisioning.


### Introduction

Land use are dynamics and change  in configuration [@phillips_opening_2017] and history of land use have important impact on provisioning of $X^2_{i,j}$ ecosystem services.

```{r}
a <- 2+4
b <- 1/sqrt(4)
c <- a/b
```

```{r chunk_name, echo=FALSE, fig.width=5, fig.height=4, results="hold",  dpi=300}

Beetle <- read.table('http://www.introductoryr.co.uk/Reproducibility/beetles.txt', header=TRUE) #Load data

plot(Beetle$taurus_pron, Beetle$taurus_horn, xlab="Pronotum width (mm)", ylab="Horn length (mm)", type="n") #Plot axes
pred <- predict(loess(taurus_horn ~ taurus_pron, span=0.5, data=Beetle),  se=TRUE) #Generate predicted vales from loess smoother
LCI <- pred$fit-2*pred$s #Lower confidence interval (approx)
UCI <- pred$fit+2*pred$s #Upper confidence interval (approx)
Xvec <- c(Beetle$taurus_pron,  rev(Beetle$taurus_pron)) #"Wraparound" X values for drawing CI band
Yvec <- c(LCI, rev(UCI)) ##"Wraparound" Y values for drawing CI band
polygon(Xvec,Yvec,col="lightblue", border=NA) #Draw the CI band
lines(Beetle$taurus_pron, pred$fit, col="darkblue") #Draw the fitted loess smoother
points(Beetle$taurus_pron, Beetle$taurus_horn) #Add the actual data points
```



```{r table1, results="asis", echo=FALSE, fig.cap='The super result table'}

mat1<-matrix(rnorm(12), ncol=3) #Generate matrix of random numbers
colnames(mat1)<-c("Header 1", "Header 2", "Header 3") # Name the columns
knitr::kable(mat1, digits=3, format="pandoc", caption = 'The super result table')

```

### References

